### 2017-10-30 manuscript.rmd
removed phylosig analysis for bract type number
added mention to B. conifera lack of tentilla in manuscript

The most complex nematocyst batteries of Cnidaria can arguably be found among the siphonophores, hanging in regularly spaced tentacle side branches called tentilla. Most hydrozoans, including the clade that contains siphonophores, bear simple tentacles (tentacles with no side branches). Is is still an open question whether the most recent common ancestor (MRCA) of Siphonophora had simple or branched tentacles. The only two siphonophore genera regarded as lacking tentilla are *Physalia* and *Apolemia*, at each side of the earliest split in the siphonophore tree, with an immediate sister group with all members bearing tentilla (*Rhizophysidae* and *{Bargmannia, Diphyes}*) (FigXX). Figure X shows the evolution of this character on the current phylogeny, indicating a most-likely tentilla bearing MRCA, with two independent losses. However, this reconstruction bears some uncertainty on the state of the MRCA, suggesting a ~30% probability of 2 independent gains of tentilla in the branches leading to *Rhizophysidae* and *{Bargmannia, Diphyes}*.

@@

```{r phylosig_bracts_declare, include=F, echo=F, message=F, warning=F}
physig_bracts_simp = phylosignal(bracts, ultratree)
physig_bracts_mult = physignal(bracts, ultratree)
```

>>>>

The most complex nematocyst batteries of Cnidaria can arguably be found among the siphonophores, hanging in regularly spaced tentacle side branches called tentilla. Most hydrozoans, including the clade that contains siphonophores, bear simple tentacles (tentacles with no side branches). Is is still an open question whether the most recent common ancestor (MRCA) of Siphonophora had simple or branched tentacles. The only two siphonophore genera regarded as lacking tentilla are *Physalia* and *Apolemia*, at each side of the earliest split in the siphonophore tree, with an immediate sister group with most members bearing tentilla (*Rhizophysidae* with the exception of *Bathyphysa conifera* and *{Bargmannia, Diphyes}*) (FigXX). Figure X shows the evolution of this character on the current phylogeny, indicating a most-likely tentilla bearing MRCA, with two independent losses. However, this reconstruction bears some uncertainty on the state of the MRCA, suggesting a ~30% probability of 2 independent gains of tentilla in the branches leading to *Rhizophysidae* and *{Bargmannia, Diphyes}*.

@@
